---
title: "Looping Files"
output: html_document
date: "2024-02-27"
---
```{r}
#Read in required libraries

##### Include Versions of libraries
#install_github('colin-olito/LoLinR')
library("ggplot2")
library("dplyr")
library("plotrix")
library("gridExtra")
library("LoLinR")
library("lubridate")
library("chron")
library('plyr')
library('tidyverse')
library('xlsx')
library('tidyr')
library('readxl')
library('magrittr')
library("segmented")
library("readr")
```



```{r}
# get the file path

setwd(here::here())
getwd()

path.p<-here::here("Data", "Respirometry_Data") #the location of all your respirametry files

```

```{r}

# bring in the respiration files
file.names<-basename(list.files(path = path.p, pattern = "csv$", recursive = TRUE)) #list all csv file names in the folder and subfolders

#basename above removes the subdirectory name from the file
file.names.full<-list.files(path = path.p, pattern = "csv$", recursive = TRUE) 

#generate a 3 column dataframe with specific column names
Photo.R<- data.frame(matrix(NA, nrow=length(file.names)*2, ncol=4))
colnames(Photo.R) <- c("ID","Intercept", "umol.L.sec","Temp.C")
View(Photo.R)

```

```{r}

#Load Sample Info 

# Read in the sample info data
morphometric_file <- here::here("Data", "Snail_Metadata", "Tegula_funebralis_Morphometric_Data.csv")
afdw_file <- here::here("Data", "Snail_Metadata", "Tegula_funebralis_AFDW.csv")
respirometry_file <- here::here("Data", "Snail_Metadata", "Respirometry_Metadata.csv")
experiment_file <- here::here("Data", "Snail_Metadata", "Experiment_Treatment_Metadata.csv")

# Read in data    
snail.data <- read_csv(morphometric_file) %>%
  select(Snail_ID:Experiment_End_Date) 
snail.afdw.data <- read_csv(afdw_file) %>%
  select(Snail_ID, Ash_Free_Dry_Weight)
respo.metadata <- read_csv(respirometry_file)
experiment.metadata <- read_csv(experiment_file)

# Joining experimental treatment, snail data, ash free dry weight, and respiration metadata
Organism.Info <- left_join(experiment.metadata, snail.data, by = "Snail_ID") %>%
  left_join(snail.afdw.data, by = "Snail_ID") %>%
  left_join(respo.metadata, by = "Snail_ID")

Organism.Info$date<-NULL

View(Organism.Info)



```



```{r}
  # for every file in list calculate O2 uptake or release rate and add the data to the Photo.R dataframe
for(i in 1:length(file.names.full)) { # for every file in list calculate O2 uptake or release rate and add the data to the Photo.R dataframe
  
  #find the lines in sample info that have the same file name that is being brought it
  FRow<-which(Organism.Info$File_ID==file.names[i])
  # read in the O2 data one by one
  Photo.Data1 <-read_csv(file.path(path.p,file.names.full[i]), skip=1) # skips the first line
  Photo.Data1 <-plyr::rename(Photo.Data1, c("Oxygen"= "Value","Temperature"="Temp"))
  #rename columns 
  Photo.Data1  <- Photo.Data1[,c("Time","Value","Temp")] #subset columns of interest
   Photo.Data1$Time <-strptime(Photo.Data1$Time, format = "%H:%M:%S") 
  Photo.Data1$Time <- strftime(Photo.Data1$Time, format = "%H:%M:%S") 
  Photo.Data1$Time <- as.POSIXct(Photo.Data1$Time,format="%H:%M:%S", tz = "") #convert time from character to time
  Photo.Data1 <- na.omit(Photo.Data1)
  
  
  #FIX TIMING START TOP OF THE HOUR 
  
  
  # clean up some of the data
  n<-dim(Photo.Data1)[1] # length of full data
  Photo.Data1 <-Photo.Data1[360:(n-3),] #start at data point ~4 minute in to avoid excess noise from start of run and remove last 3 lines containing text
  n<-dim(Photo.Data1)[1] #list length of trimmed data
  Photo.Data1$sec <- (1:n) #set seconds by one from start to finish of run in a new column
  
  #Save plot prior to and after data thinning to make sure thinning is not too extreme
  rename <- file.names[i] # remove all the extra stuff in the file name
   pdf(here::here("Data", "Thinned_Respirometry_Data", paste0(rename, "_thinning.pdf")))
  # open the graphics device
  
  par(omi=rep(0.3, 4)) #set size of the outer margins in inches
  par(mfrow=c(1,2)) #set number of rows and columns in multi plot graphic
  plot(Value ~ sec, data=Photo.Data1 , xlab='Time (seconds)', ylab=expression(paste(' O'[2],' (',mu,'mol/L)')), type='n', axes=FALSE) #plot (empty plot to fill) data as a function of time
  usr  <-  par('usr') # extract the size of the figure margins
  rect(usr[1], usr[3], usr[2], usr[4], col='grey90', border=NA) # put a grey background on the plot
  whiteGrid() # make a grid
  box() # add a box around the plot
  points(Photo.Data1 $Value ~ Photo.Data1 $sec, pch=16, col=transparentColor('dodgerblue2', 0.6), cex=1.1)
  axis(1) # add the x axis
  axis(2, las=1) # add the y-axis
  

  
  # Thin the data to make the code run faster
  Photo.Data.orig<-Photo.Data1#save original unthinned data
  Photo.Data1 <-  thinData(Photo.Data1 ,by=20)$newData1 #thin data by every 5 points for all the O2 values
  Photo.Data1$sec <- as.numeric(rownames(Photo.Data1 )) #maintain numeric values for time
  Photo.Data1$Temp<-NA # add a new column to fill with the thinned data
  Photo.Data1$Temp <-  thinData(Photo.Data.orig,xy = c(1,3),by=20)$newData1[,2] #thin data by every 5 points for the temp values
  
  # plot the thinned data
  plot(Value ~ sec, data=Photo.Data1 , xlab='Time (seconds)', ylab=expression(paste(' O'[2],' (',mu,'mol/L)')), type='n', axes=FALSE) #plot thinned data
  usr  <-  par('usr')
  rect(usr[1], usr[3], usr[2], usr[4], col='grey90', border=NA)
  whiteGrid()
  box()
  points(Photo.Data1 $Value ~ Photo.Data1 $sec, pch=16, col=transparentColor('dodgerblue2', 0.6), cex=1.1)
  axis(1)
  axis(2, las=1)
  ##Olito et al. 2017: It is running a bootstrapping technique and calculating the rate based on density
  #option to add multiple outputs method= c("z", "eq", "pc")
  Regs  <-  rankLocReg(xall=Photo.Data1$sec, yall=Photo.Data1$Value, alpha=0.5, method="pc", verbose=TRUE)  
  
  # add the regression data
  plot(Regs)
  dev.off()
  
  # fill in all the O2 consumption and rate data
  Photo.R[i,2:3] <- Regs$allRegs[1,c(4,5)] #inserts slope and intercept in the dataframe
  Photo.R[i,1] <- rename #stores the file name in the Date column
  Photo.R[i,4] <- mean(Photo.Data1$Temp, na.rm=T)  #stores the Temperature in the Temp.C column

}
  

View(Photo.R)
write_csv(Photo.R, here::here("Data", "Thinned_Respirometry_Data", "Respirometry.Rates.Dataset.csv"))

```

```{r}
```

```{r}
#join dataframes
Photo.R<-left_join(Photo.R, Organism.Info)
View(Photo.R)
```

```{r}
# Calculate P and R rate
#Convert sample volume to mL
Photo.R$volume <- Photo.R$volume.mls/1000 #calculate volume

#Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
Photo.R$umol.sec <- Photo.R$umol.L.sec*Photo.R$volume

#Account for blank rate by temperature
#convert character columns to factors
Photo.R <- Photo.R %>%
  mutate_if(sapply(., is.character), as.factor)
View(Photo.R)

```

```{r}
#make the blank column a factor
Photo.R$BLANK<-ifelse(Photo.R$treatment=='BLANK', 1,0)
Photo.R$BLANK<-as.factor(Photo.R$BLANK)

photo.blnk <- aggregate(umol.sec ~ genotype*temp.Cat*light_dark*run*BLANK, data=Photo.R, mean)

# pull out only the blanks
#photo.blnk<-photo.blnk[photo.blnk$Species=='BK',]
photo.blnk<-photo.blnk[photo.blnk$BLANK==1,]
# remove the species column and join with the full data set
photo.blnk$genotype<-NULL
# remove the blank column
photo.blnk$BLANK<-NULL

colnames(photo.blnk)[4]<-'blank.rate' # rename the blank rate 
View(photo.blnk)


#write.csv(photo.blnk,"C:/Github/TPC_Acropora/R_output_Data_Frames/photo.blnk.csv")

# join the blank data with the rest of the data
Photo.R<-left_join(Photo.R, photo.blnk)
View(Photo.R)

#write.csv(Photo.R, "C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.R.blnk.csv")

```

```{r}
# subtract the blanks######################
Photo.R$umol.sec.corr<-Photo.R$umol.sec-Photo.R$blank.rate

View(Photo.R)

#### Normalize to SA (surface area)#####

Photo.R$umol.cm2.hr <- (Photo.R$umol.sec.corr*3600)/Photo.R$surf.area.cm2 #mmol cm-2 hr-1

#Photo.R<-Photo.R[complete.cases(Photo.R),] # remove NAs and blanks
#Photo.R <- na.omit(Photo.R)
Photo.R<-Photo.R[Photo.R$BLANK==0,]
```

```{r}

#Calculate net P and R
#make ifelse statements to assign light treatments as NP and dark treatments as resp
#light will be assigned NP for net photosynthesis 

Photo.R$rate.type <-ifelse(Photo.R$light_dark=='light', "NP", "R")
Photo.R$rate.type<-as.factor(Photo.R$rate.type)
View(Photo.R)

#rename coral ID
Photo.R$individual.ID <- str_split(Photo.R$fragment.ID, "D", n = Inf, simplify = TRUE)[,1]

Photo.R$individual.ID <- as.factor(Photo.R$individual.ID)

Photo.R$individual.ID<-str_sub(Photo.R$individual.ID , 1, str_length(Photo.R$individual.ID)-1)

Photo.R<-na.omit(Photo.R)

#write.csv(Photo.R,"C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R.csv")

# added a column in excel for trial without the D for dark trials- re-read in dataframe below 
Photo.RNP_R <-read.csv("C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R_trial_ed.csv") 
Photo.Rt<-Photo.RNP_R
Photo.Rt$X<-NULL
```


Calculate GP

```{r}


library(Rmisc)
sumE = summarySE(Photo.Rt,
                measurevar="Temp.C",            groupvars=c('treatment', 'genotype','temp.Cat', 'fragment.ID'))
sumE <- na.omit(sumE)
sumE%>% arrange(fragment.ID)
#Temp.C<-sumE$Temp.C
# average Temp.C for both trials and add to dataframes

#get Pnet and R into same coloumn

Pnet<-subset(Photo.Rt,rate.type=="NP")%>%
  dplyr::select(Temp.C, temp.Cat ,trial,treatment, genotype,fragment.ID, umol.cm2.hr,rate.type, individual.ID)

Pnet$NP<-Pnet$umol.cm2.hr
Pnet$umol.cm2.hr=NULL
Pnet$rate.type=NULL
sumE%>% arrange(desc(fragment.ID))
Pnet<-left_join(Pnet,sumE, by= c("treatment", "fragment.ID", "temp.Cat"))

#Pnet$avgTemp<-NULL
#Pnet[["Temp.C"]] <- sumE$Temp.C
Pnet$Temp.C.x <-NULL
Pnet$ci <-NULL
Pnet$se <-NULL
Pnet$sd <-NULL
Pnet$N <-NULL
Pnet$genotype.y <-NULL
Pnet$Temp.C<-Pnet$Temp.C.y
Pnet$Temp.C.y <-NULL
Pnet$genotype<-Pnet$genotype.x
Pnet$genotype.x <-NULL
as.numeric(Pnet$Temp.C)

Rdark<-subset(Photo.Rt,rate.type=="R")%>%
  dplyr::select( Temp.C, temp.Cat, trial,treatment, genotype,fragment.ID, umol.cm2.hr,rate.type, individual.ID)

Rdark$R<-Rdark$umol.cm2.hr
Rdark$rate.type=NULL
Rdark$umol.cm2.hr=NULL
Rdark<-left_join(Rdark,sumE, by= c("treatment", "fragment.ID", "temp.Cat"))
Rdark$Temp.C.x <-NULL
Rdark$ci <-NULL
Rdark$se <-NULL
Rdark$sd <-NULL
Rdark$N <-NULL
Rdark$genotype.y <-NULL
Rdark$Temp.C<-Rdark$Temp.C.y
Rdark$Temp.C.y <-NULL
Rdark$genotype<-Rdark$genotype.x
Rdark$genotype.x <-NULL
as.numeric(Rdark$Temp.C)


Photo.RGP<-left_join(Pnet, Rdark)
View(Photo.RGP)

#write.csv(Photo.RGP,"C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RGPtemp_corrected.csv")

#ca
#Photo.RNP_R <-read.csv("C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R.csv") 
#Photo.R<-Photo.RNP_R
#Photo.R$X<-NULL

#(respiration is negative so Pnet-Res=GP)
photo.GP <- Photo.RGP %>%
  group_by(fragment.ID) %>%
  mutate(GP = NP-R)

## Find any negative NP's and make them 0's
lessthan <- which(photo.GP$GP < 0) # No negative GP rates
#photo.GP$GP[lessthan] <- 0
View(photo.GP)
#rearrange columns if wanted
#photo.GP<- photo.GP[c(1,2,3,4,5,6,7,8,10,9,11,12)]

data_long <- gather(photo.GP, rate.type, umol.cm2.hr, NP, R, GP, factor_key=TRUE)
View(data_long)

#write.csv(photo.GP,"C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R_GPtempcorrect.csv")
#write.csv(data_long,"C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R_GPlongtempcorrect.csv")
```


## isolate GP and R and log values 
```{r}

#data_long<-read.csv("C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R_GPlongtempcorrect.csv")
##data_long<-filter(mydata, rate.type !="NP") 

mydata<-data_long

mydatalog$umol.cm2.hr<-as.numeric(as.character(mydatalog$umol.cm2.hr))

mydata<-filter(mydata, rate.type !="NP") 

mydataP<-subset(mydata,rate.type=="GP")
mydataR<-subset(mydata,rate.type=="R")

#Take absolute values of Respiration to log it, then combine dataframes and log both R and GP
mydataR$umol.cm2.hr<-abs(mydataR$umol.cm2.hr)
mydatalog<-rbind(mydataP,mydataR)

mydatalog$log.rate <- log(mydatalog$umol.cm2.hr + 1) 

mydatalog$Temp.C<-as.numeric(as.character(mydatalog$Temp.C))

### Add 1C to the Temp.C as the APEX was 1C below temperature recordings compared to temperature probes used to validate APEX
mydatalog$Temp.C<-(mydatalog$Temp.C + 1)

mydatalog<-mydatalog%>%
  plyr::mutate(K=mydatalog$Temp.C + 273.15)

mydatalog$temp.Cat<-factor(mydatalog$temp.Cat)

#save
#write.csv(mydatalog,"C:/Github/TPC_Acropora/R_output_Data_Frames/mydatalogtempcorr.csv")
```


```{r}

rawslope<- ggplot(mydatalog, aes(x=Temp.C, y=log.rate, group=treatment, color=treatment)) + 
  geom_smooth(se=TRUE, span= 1.5) +
  geom_point(size=2,position=position_dodge(0.5))+
  #geom_errorbar(aes(ymin=PR-sd, ymax=PR+sd), width=.2,
              # position=position_dodge(0.5))+
  labs(y="log.rate", x = "Temperature (ºC)")+
  theme_classic() +
  facet_wrap(~rate.type*genotype)
rawslope

rawslope2<- ggplot(mydatalog, aes(x=Temp.C, y=log.rate, group=treatment, color=treatment)) + 
  geom_smooth(se=TRUE, span= 1.5) +
  geom_point(size=2,position=position_dodge(0.5))+
  #geom_errorbar(aes(ymin=PR-sd, ymax=PR+sd), width=.2,
              # position=position_dodge(0.5))+
  labs(y="log.rate", x = "Temperature (ºC)")+
  theme_classic() +
  facet_wrap(~rate.type*treatment)
rawslope2

GP<-ggplot(mydatalog, aes(x=Temp.C, y=log.rate, col = rate.type, shape= genotype))+
  geom_point()+ 
  geom_smooth(se=TRUE, span= 1.5)+ 
  theme_classic () +
  ylim(-2,4)+  
  facet_wrap(~ treatment)
GP
```

```{r}
mPGPsp<-lm(log.rate~genotype*treatment*temp.Cat,mydatalog)
summary(mPGPsp)
anova(mPGPsp)
```

```{r}

#Calculate means from raw NP, R, and GP umo.cm2.hr on it
AllMeansT <- ddply(photo.GP, c('treatment'), summarise,
                   #pnet
                   Pnet.mean= mean(NP, na.rm=T), #mean pnet
                   N = sum(!is.na(NP)), # sample size
                   Pnet.se = sd(NP, na.rm=T)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(R, na.rm=T), #mean rdark
                   Rdark.se = sd(R, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GP, na.rm=TRUE),
                   Pgross.se = sd(GP, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansT)

AllMeansG <- ddply(photo.GP, c('genotype'), summarise,
                   #pnet
                   Pnet.mean= mean(NP, na.rm=T), #mean pnet
                   N = sum(!is.na(NP)), # sample size
                   Pnet.se = sd(NP, na.rm=T)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(R, na.rm=T), #mean rdark
                   Rdark.se = sd(R, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GP, na.rm=TRUE),
                   Pgross.se = sd(GP, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansG)

AllMeansI <- ddply(photo.GP, c('treatment', 'fragment.ID'), summarise,
                   #pnet
                   Pnet.mean= mean(NP, na.rm=T), #mean pnet
                   N = sum(!is.na(NP)), # sample size
                   Pnet.se = sd(NP, na.rm=T)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(R, na.rm=T), #mean rdark
                   Rdark.se = sd(R, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GP, na.rm=TRUE),
                   Pgross.se = sd(GP, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansI) # all temperatures together-

#write.csv(AllMeansT,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansTtempcorr.csv")
#write.csv(AllMeansG,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansGtempcorr.csv")
#write.csv(AllMeansI,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansItempcorr.csv")
```

NP by genotype, treatment and interaction
```{r}

p<- ggplot(AllMeansG, aes(x=genotype, y=Pnet.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
p

p2<- ggplot(AllMeansT, aes(x=treatment, y=Pnet.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p2

p3<- ggplot(AllMeansI, aes(x=treatment, y=Pnet.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p3

p4<- ggplot(AllMeansI, aes(x=treatment, y=Pnet.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p4
```

R by genotype, treatment and interaction
```{r}

pr<- ggplot(AllMeansG, aes(x=genotype, y=Rdark.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
pr

pr2<- ggplot(AllMeansT, aes(x=treatment, y=Rdark.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr2

pr3<- ggplot(AllMeansI, aes(x=treatment, y=Rdark.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr3

pr4<- ggplot(AllMeansI, aes(x=treatment, y=Rdark.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr4
```


GP by genotype, treatment and interaction
```{r}

pg<- ggplot(AllMeansG, aes(x=genotype, y=Pgross.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("GP", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
pg

pg2<- ggplot(AllMeansT, aes(x=treatment, y=Pgross.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste(" GP", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg2

pg3<- ggplot(AllMeansI, aes(x=treatment, y=Pgross.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("GP", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg3

pg4<- ggplot(AllMeansI, aes(x=treatment, y=Pgross.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("GP", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg4
```


#Calculate (logged)means from Photo.GP with ALL NP, R, and GP 

```{r}

Photo.GP<-photo.GP
Photo.GP$Temp.C<-(Photo.GP$Temp.C + 1)


Photo.GP$NPlog.rate <- log(Photo.GP$NP + 1) 
Photo.GP$Rabs<-abs(Photo.GP$R)
Photo.GP$Rlog.rate <- log(Photo.GP$Rabs + 1) 
Photo.GP$GPlog.rate <- log(Photo.GP$GP + 1) 

#write.csv(Photo.GP,"C:/Github/TPC_Acropora/R_output_Data_Frames/Photo.RNP_R_GP_logtempcorr.csv")


AllMeansTLog <- ddply(Photo.GP, c('treatment'), summarise,
                   #pnet
                   Pnet.mean= mean(NPlog.rate, na.rm=T), #mean pnet
                   N = sum(!is.na(NPlog.rate)), # sample size
                   Pnet.se = sd(NPlog.rate)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(Rlog.rate, na.rm=T), #mean rdark
                   Rdark.se = sd(Rlog.rate, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GPlog.rate, na.rm=TRUE),
                   Pgross.se = sd(GPlog.rate, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansTLog)

AllMeansGLog <- ddply(Photo.GP, c('genotype'), summarise,
                   #pnet
                   Pnet.mean= mean(NPlog.rate, na.rm=T), #mean pnet
                   N = sum(!is.na(NPlog.rate)), # sample size
                   Pnet.se = sd(NPlog.rate, na.rm=T)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(Rlog.rate, na.rm=T), #mean rdark
                   Rdark.se = sd(Rlog.rate, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GPlog.rate, na.rm=TRUE),
                   Pgross.se = sd(GPlog.rate, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansGLog)

AllMeansILog <- ddply(Photo.GP, c('treatment', 'fragment.ID'), summarise,
                   #pnet
                   Pnet.mean= mean(NPlog.rate, na.rm=T), #mean pnet
                   N = sum(!is.na(NPlog.rate)), # sample size
                   Pnet.se = sd(NPlog.rate, na.rm=T)/sqrt(N), #SE
                   #Rdark
                   Rdark.mean= mean(Rlog.rate, na.rm=T), #mean rdark
                   Rdark.se = sd(Rlog.rate, na.rm=T)/sqrt(N), #SE
                   #Pgross
                   Pgross.mean  = mean(GPlog.rate, na.rm=TRUE),
                   Pgross.se = sd(GPlog.rate, na.rm=TRUE)/sqrt(N),
                   Temp.mean = mean(Temp.C, na.rm=TRUE),
                   Temp.se = sd(Temp.C,na.rm=TRUE)/sqrt(N)
)

View(AllMeansILog)

#write.csv(AllMeansTLog,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansTLogtempcorr.csv")
#write.csv(AllMeansGLog,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansGLogtempcorr.csv")
#write.csv(AllMeansILog,"C:/Github/TPC_Acropora/R_output_Data_Frames/AllMeansILogtempcorr.csv")
```

NP by genotype, treatment and interaction
```{r}

pl<- ggplot(AllMeansGLog, aes(x=genotype, y=Pnet.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ", "log",mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
pl

p2l<- ggplot(AllMeansTLog, aes(x=treatment, y=Pnet.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ","log", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p2l

p3l<- ggplot(AllMeansILog, aes(x=treatment, y=Pnet.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ","log", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p3l

p4l<- ggplot(AllMeansILog, aes(x=treatment, y=Pnet.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pnet.mean-Pnet.se, ymax=Pnet.mean+Pnet.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("NP ","log", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
p4l
```

R by genotype, treatment and interaction
```{r}

prl<- ggplot(AllMeansGLog, aes(x=genotype, y=Rdark.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ", "log",mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
prl

pr2l<- ggplot(AllMeansTLog, aes(x=treatment, y=Rdark.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ","log", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr2l

pr3l<- ggplot(AllMeansILog, aes(x=treatment, y=Rdark.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("R ","log", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr3l

pr4l<- ggplot(AllMeansILog, aes(x=treatment, y=Rdark.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Rdark.mean-Rdark.se, ymax=Rdark.mean+Rdark.se), width=.2,
                position=position_dodge(0.5))+
  geom_text(aes(label=ifelse(Rdark.mean>0.75,as.character(fragment.ID),'')),hjust=0,vjust=2)+
geom_text(aes(label=fragment.ID),hjust=0, vjust=0)+
  ylab(expression(paste("R ","log",mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pr4l

```


GP by genotype, treatment and interaction
```{r}

pgl<- ggplot(AllMeansGLog, aes(x=genotype, y=Pgross.mean, group=genotype, color=genotype)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste("GP", "log",mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Genotype")+
  theme_classic() 
pgl

pg2l<- ggplot(AllMeansTLog, aes(x=treatment, y=Pgross.mean, group=treatment, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
  ylab(expression(paste(" GP log ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg2l

pg3l<- ggplot(AllMeansILog, aes(x=treatment, y=Pgross.mean, group=treatment, color=fragment.ID)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
    geom_text(aes(label=ifelse(Pgross.mean>0.8,as.character(fragment.ID),'')),hjust=0,vjust=2)+
  ylab(expression(paste("GP log ", mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg3l

pg4l<- ggplot(AllMeansILog, aes(x=treatment, y=Pgross.mean, group=fragment.ID, color=treatment)) + 
    geom_point(size=2,position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Pgross.mean-Pgross.se, ymax=Pgross.mean+Pgross.se), width=.2,
                position=position_dodge(0.5))+
    geom_text(aes(label=ifelse(Pgross.mean>0.8,as.character(fragment.ID),'')),hjust=0,vjust=2)+
  ylab(expression(paste("GP log ",mu,O[2],"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Mean rate + SEM")+
  xlab("Treatment")+
  theme_classic() 
pg4l

#M50Cd had very high rates both NP and R values for ALL temperatures. REMOVE AS outlier 
```

Data Manipulation saved in TPC_acropora folder 2021

Next rmark down for creating TPC and parameter estimates is "Acropora_TPC_Parameter_StatAnalysis_Final_2_24_2021"
