---
title: "Respirometry_Thermal_Performance_Script"
output: 
  pdf_document:
    latex_engine: pdflatex
date: "2023-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(LoLinR)
library(rTPC)
library(nls.multstart)
library(minpack.lm)
library(boot)
library(car)
library(broom)
library(patchwork)
library(ggplot2)
library(ggimage)
library(ggrepel)
library(gt)
library(gtExtras)
library(gridExtra)
library(nlstools)
library(ggpmisc)
```

# Loading Data

```{r}
#Reading in organism morphometric data 
snail.data <- read_csv(here::here("Data", "Snail_Metadata", "Tegula_funebralis_Morphometric_Data.csv")) %>% 
  select(Snail_ID:Experiment_End_Date)

#Reading in ash free dry weight data
snail.afdw.data <- read_csv(here::here("Data", "Snail_Metadata","Tegula_funebralis_AFDW.csv"))%>% 
  select(Snail_ID, Dry_Weight_g, Ash_Content_g, Ash_Free_Dry_Weight)

#Reading in respirometry metadata
respo.metadata <- read_csv(here::here("Data", "Snail_Metadata","Respirometry_Metadata.csv"))

#Reading in experimental treatment metadata 
experiment.metadata <- read_csv(here::here("Data", "Snail_Metadata","Experiment_Treatment_Metadata.csv"))

#loading tegula icon in
image=here::here("Images", "Tegula_funebralis_icon.png")

# Reading in Long Term Means 
long.term.filtered.means <- read_csv(here::here("Data", "Mesocosm_Data", "Mesocosm_Temp_Filtered_Means.csv"))
long.term.means <- read_csv(here::here("Data", "Mesocosm_Data", "Mesocosm_Temp_Means.csv"))

#filtering out irresponsible snails & snails not run in respirometry
experiment.data <- experiment.data %>% 
  filter(Snail_ID != 36,
         Snail_ID != 43,
         Snail_ID != 72,
         Snail_ID != 61,
         #Snail_ID != 67,
         #Snail_ID != 52
         ) # mortality (not responsive to forceps)
```


```{r}
# Ash Free Dry Weight Calculation and Comparison to Paine 1971
#AFDW = DW * (1 - (Ash/100))
#Percent Ash = (Ash Free Dry Weight / Initial Blotted Wet Mass) * 100
#Percent Ash Reported by Paine 1971 ~9.02%

snail.afdw.data <- snail.afdw.data %>% 
  mutate(Ash_Free_Dry_Weight=(Dry_Weight_g*(1-(Ash_Content_g/100)))) #overwritten as CSV
  
snail.data <- left_join(snail.data, snail.afdw.data, by = join_by(Snail_ID))

snail.data <- snail.data %>% 
  mutate(Percent_Ash=((Ash_Free_Dry_Weight/Initial_Blotted_Wet_Mass_g)*100),
         Percent_Ash_Paine_1971= 9.02,
         Expected_Ash_Free_Dry_Weight=Initial_Blotted_Wet_Mass_g*(Percent_Ash_Paine_1971/100)) %>%
  select(Snail_ID, Initial_Blotted_Wet_Mass_g, Final_Blotted_Wet_Mass_g, Ash_Free_Dry_Weight, Percent_Ash,
         Expected_Ash_Free_Dry_Weight) %>% 
  na.omit()

# AFDW Comparison
mean.afdw <- snail.data %>% 
  dplyr::summarize(Mean_AFDW = mean(Ash_Free_Dry_Weight, na.rm = TRUE),
         Mean_Expected_AFDW = mean(as.numeric(Expected_Ash_Weight), na.rm = TRUE))

```

```{r}

# Exploring Snail Measurement Metrics 

#running linear regression for snail measurements (Initial_Blotted_Wet_Mass_g versus Ash_Free_Dry_Weight)
lm.snail.data <- lm(Initial_Blotted_Wet_Mass_g ~ Ash_Free_Dry_Weight, data = snail.data)

plot(lm.snail.data)
summary(lm.snail.data)

# Extracting R-squared value
rsquared <- summary(lm.snail.data)$r.squared

# Plotting the data points
plot(snail.data$Ash_Free_Dry_Weight, snail.data$Initial_Blotted_Wet_Mass_g, 
     xlab = "Ash Free Dry Weight", ylab = "Initial Blotted Wet Mass (g)",
     main = "Linear Regression of Snail Measurements (Initial Blotted Wet Mass vs. Ash Free Dry Weight)")

# Adding the regression line
abline(lm.snail.data, col = "blue")

# Adding text for R-squared value
text(x = min(snail.data$Ash_Free_Dry_Weight), y = max(snail.data$Initial_Blotted_Wet_Mass_g), 
     labels = paste("R^2 =", round(rsquared, 3)), pos = 2)

# Adding legend for regression line
legend("topleft", legend = paste("Regression Line (R^2 =", round(rsquared, 3), ")", sep = ""), col = "blue", lty = 1)

```



```{r}

snail.measurement.data <- experiment.data %>% 
  filter(Identity == 'Treatment')
  
shell.width.range <- range(snail.measurement.data$Shell_Width_mm)

# Calculate the mean Shell_Width_mm
mean_width <- mean(snail.measurement.data$Shell_Width_mm, na.rm = TRUE)

# Calculate the standard deviation
sd_width <- sd(snail.measurement.data$Shell_Width_mm, na.rm = TRUE)

cat("Shell Width Range:", shell.width.range, "\n")
cat("Mean Shell Width:", mean_width, "\n")
cat("Standard Deviation:", sd_width, "\n")

  
shell.height.range <- range(snail.measurement.data$Shell_Height_mm)

# Calculate the mean Shell_Width_mm
mean_height <- mean(snail.measurement.data$Shell_Height_mm, na.rm = TRUE)

# Calculate the standard deviation
sd_height <- sd(snail.measurement.data$Shell_Height_mm, na.rm = TRUE)

cat("Shell Height Range:", shell.height.range, "\n")
cat("Mean Shell Height:", mean_height, "\n")
cat("Standard Deviation:", sd_height, "\n")


snail.initial.mass.range <- range(snail.measurement.data$Initial_Blotted_Wet_Mass_g)

# Calculate the mean Shell_Width_mm
mean_initial_mass <- mean(snail.measurement.data$Initial_Blotted_Wet_Mass_g, na.rm = TRUE)

# Calculate the standard deviation
sd_initial_mass <- sd(snail.measurement.data$Initial_Blotted_Wet_Mass_g, na.rm = TRUE)

cat("Snail Initial Mass Range:", snail.initial.mass.range, "\n")
cat("Mean Snail Initial Mass:", mean_initial_mass, "\n")
cat("Standard Deviation:", sd_initial_mass, "\n")

snail.final.mass.range <- range(snail.measurement.data$Final_Blotted_Wet_Mass_g)

# Calculate the mean Shell_Width_mm
mean_final_mass <- mean(snail.measurement.data$Final_Blotted_Wet_Mass_g, na.rm = TRUE)

# Calculate the standard deviation
sd_final_mass <- sd(snail.measurement.data$Final_Blotted_Wet_Mass_g, na.rm = TRUE)

cat("Snail Final Mass Range:", snail.final.mass.range, "\n")
cat("Mean Snail Final Mass:", mean_final_mass, "\n")
cat("Standard Deviation:", sd_final_mass, "\n")


snail.volume.range <- range(snail.measurement.data$Organism_Volume_mL)

# Calculate the mean Shell_Width_mm
mean_volume <- mean(snail.measurement.data$Organism_Volume_mL, na.rm = TRUE)

# Calculate the standard deviation
sd_volume <- sd(snail.measurement.data$Organism_Volume_mL, na.rm = TRUE)

cat("Snail Volume Range:", snail.volume.range, "\n")
cat("Mean Snail Volume:", mean_volume, "\n")
cat("Standard Deviation:", sd_volume, "\n")



```



```{r Reading Respirometry Data and Wrangling Data}
# Reading and Merging Data 
respirometry.data.summarized <- read_csv(here("Data", "Thinned_Respirometry_Data", "Respirometry.Data.csv"))

#Empty chamber volume (650 mL)
Chamber_Volume <- 650

#Joining respiration data with the data 
joined.respo.dataset <- left_join(experiment.data, respirometry.data.summarized, by = join_by(File_ID))


#calcucating chamber volumes
joined.respo.dataset <- joined.respo.dataset %>%              
mutate(Volume_mL=Chamber_Volume-Organism_Volume_mL, #calculating chamber water volume by subtracting organism volume
       umolO2.sec = (umolO2.L.sec/1000)*Volume_mL) #converting from L to mL and standardizing to water volume

# Calculating control respiration rates
respo.control.data <- joined.respo.dataset %>%
  filter(Identity=="Control") %>% #filtering for blanks
  group_by(Temp_Treatment, pH_Treatment, Identity) %>% #grouping by treatments
  summarise(umolO2.sec = mean(umolO2.sec, na.rm=TRUE)) %>% #means for blanks and organisms 
  select(blank.rate = umolO2.sec) #selecting for only blank rates

#joining summarized control respiration data to full respiration dataset 
respo.dataset <- left_join(joined.respo.dataset, respo.control.data)

# converting from umolO2/sec to umolO2/hour and normalizing to ash free dry weight (grams)
respo.rates.dataset <- respo.dataset %>% 
  mutate(
    umolO2.sec.uncorrected = -(umolO2.sec),
    umolO2.sec.corrected = -(umolO2.sec - blank.rate), # subtract the blank rates from the raw rates
    umolO2.gram.hr.uncorrected = umolO2.sec.uncorrected * 3600 / Ash_Free_Dry_Weight,
    umolO2.gram.hr.corrected = umolO2.sec.corrected * 3600 / Ash_Free_Dry_Weight) %>% 
  #correcting for negative respiration rates and for values that fall below 0
  mutate(
    umolO2.gram.hr.corrected = ifelse(umolO2.gram.hr.corrected < 0, 0, umolO2.gram.hr.corrected), 
    umolO2.gram.hr.uncorrected = ifelse(umolO2.gram.hr.uncorrected < 0, 0, umolO2.gram.hr.uncorrected)) %>% 
  filter(Identity == "Treatment") %>% 
  select(Snail_ID, Temp_Treatment, pH_Treatment, umolO2.sec.uncorrected, umolO2.sec.corrected, umolO2.gram.hr.corrected,  
         umolO2.gram.hr.uncorrected, Temp.C, Volume_mL)

as_tibble(respo.rates.dataset)

write_csv(respo.rates.dataset, here("Data", "Thinned_Respirometry_Data", "Respiration.Rates.Dataset.csv"))
```

```{r}

# umolO2 per second to joules per second corrected for background respiration (Organism respiration- Background respiration, no weight normalization)
umol.O2.per.second.per.snail <- respo.rates.dataset %>% 
  select(Snail_ID, umolO2.sec.corrected, Temp_Treatment, pH_Treatment, Temp.C) %>% 
  mutate(umolO2.sec.corrected  = umolO2.sec.corrected  * 1000) #converst to L

#conversion of micro moles of O2 per second to micro moles of O2 per hour
umol.O2.per.hour.per.snail <- umol.O2.per.second.per.snail %>% 
  mutate(mmolO2.hr.per.snail = umolO2.sec.corrected * 3600)
  
#conversion of micro moles of O2 per hour to moles of O2 per hour
mol.O2.per.hour.per.snail <- umol.O2.per.hour.per.snail %>% 
  mutate(molO2.hr.per.snail = mmolO2.hr.per.snail/1000000)

#moles of O2 per hour (mol/hr) times the molecular weight of oxygen (32 g/mol) to get grams of O2 per hour
gram.O2.per.hour.per.snail <- mol.O2.per.hour.per.snail %>% 
  mutate(g.O2.hr.per.snail = molO2.hr.per.snail * 32)

#convert from gram of O2 to milligrams of O2
mg.O2.per.hour.per.snail <- gram.O2.per.hour.per.snail %>% 
  mutate(mg.O2.hr.per.snail = molO2.hr.per.snail * 1000)

#cellular respiration, oxygen (O2) is consumed to produce energy in the form of adenosine triphosphate (ATP)
# C6H12O6 + 6O2 → 6CO2 + 6H2O + energy (as ATP)

# Define the conversion factor
conversion_factor <- 14.14 # Energy equivalent of 1 mg of O2 consumed (Elliott and Davison, 1975)

#multiply milligram of O2 per hr times conversion factor of 14.14 J per mg O2− (Elliott and Davison, 1975) to get joules O2 per hour
#grams of O2 per hour (g/hr) times the energy produced per gram of oxygen 
joules.per.hour.per.snail <- mg.O2.per.hour.per.snail %>% 
  mutate(J.hr.per.snail = mg.O2.hr.per.snail * conversion_factor)

#joules per hour per snail to kilojoules per hour per snail
kj.per.hour.per.snail <- joules.per.hour.per.snail %>% 
  mutate(kJ.hr.per.snail = J.hr.per.snail / 1000) #thsi is in mL

joule.rates.dataset <- kj.per.hour.per.snail
```








```{r }

# umolO2 per second to joules per second corrected for background respiration (Organism respiration- Background respiration, no weight normalization)
umol.O2.per.second.per.snail <- respo.rates.dataset %>% 
  select(Snail_ID, umolO2.sec.corrected, Temp_Treatment, pH_Treatment, Temp.C) %>% 
  mutate(umolO2.sec.corrected  = umolO2.sec.corrected  * 1000) #converst to L

#conversion of micro moles of O2 per second to micro moles of O2 per hour
umol.O2.per.hour.per.snail <- umol.O2.per.second.per.snail %>% 
  mutate(mmolO2.hr.per.snail = umolO2.sec.corrected * 3600)
  
#conversion of micro moles of O2 per hour to moles of O2 per hour
mol.O2.per.hour.per.snail <- umol.O2.per.hour.per.snail %>% 
  mutate(molO2.hr.per.snail = mmolO2.hr.per.snail/1000000)

#moles of O2 per hour (mol/hr) times the molecular weight of oxygen (32 g/mol) to get grams of O2 per hour
gram.O2.per.hour.per.snail <- mol.O2.per.hour.per.snail %>% 
  mutate(g.O2.hr.per.snail = molO2.hr.per.snail * 32)

#convert from gram of O2 to milligrams of O2
mg.O2.per.hour.per.snail <- gram.O2.per.hour.per.snail %>% 
  mutate(mg.O2.hr.per.snail = molO2.hr.per.snail * 1000)

#cellular respiration, oxygen (O2) is consumed to produce energy in the form of adenosine triphosphate (ATP)
# C6H12O6 + 6O2 → 6CO2 + 6H2O + energy (as ATP)

# Define the conversion factor
conversion_factor <- 14.14 # Energy equivalent of 1 mg of O2 consumed (Elliott and Davison, 1975)

#multiply milligram of O2 per hr times conversion factor of 14.14 J per mg O2− (Elliott and Davison, 1975) to get joules O2 per hour
#grams of O2 per hour (g/hr) times the energy produced per gram of oxygen 
joules.per.hour.per.snail <- mg.O2.per.hour.per.snail %>% 
  mutate(J.hr.per.snail = mg.O2.hr.per.snail * conversion_factor)

#joules per hour per snail to kilojoules per hour per snail
kj.per.hour.per.snail <- joules.per.hour.per.snail %>% 
  mutate(kJ.hr.per.snail = J.hr.per.snail / 1000) #thsi is in mL

joule.rates.dataset <- kj.per.hour.per.snail %>% 
  mutate(Temp_Treatment=as.factor(Temp_Treatment),
         pH_Treatment=as.factor(pH_Treatment)) #converting to joules per second

```

```{r}
# Perform a two-way ANOVA
anova_result <- anova(lm(J.hr.per.snail ~ Temp_Treatment * pH_Treatment, data = joule.rates.dataset))

# Print the ANOVA table
print(anova_result)
# significant p value (1.101e-08 ***) for temp treatment but not for ph treatment (0.1235)

# Perform a Tukey's HSD test
tukey_result <- TukeyHSD(aov(J.hr.per.snail ~ Temp_Treatment * pH_Treatment, data = joule.rates.dataset))

# Print the Tukey's HSD test
print(tukey_result)

```

```{r}

# joule rate summary statistics 
joule.rates.summary <- joule.rates.dataset %>%
  filter(pH_Treatment != "Sump") %>%
  group_by(Temp_Treatment, pH_Treatment) %>%
  summarize(
    Mean_joule_sec = mean(J.hr.per.snail),
    Median_joule_sec = median(J.hr.per.snail),
    Min_joule_sec = min(J.hr.per.snail),
    Max_joule_sec = max(J.hr.per.snail),
    SD_joule_sec = sd(J.hr.per.snail),
    SE_joule_sec = sd(J.hr.per.snail) / sqrt(n()),
    N_joule_sec = n()
  ) 
  
# Print the ANOVA table
print(joule.rates.summary)

mean_joule_sec <- joule.rates.summary %>%
  group_by(Temp_Treatment,pH_Treatment) %>%
  select(Temp_Treatment, pH_Treatment, Mean_joule_sec) 

# Pivot the data to have Temp_Treatment as rows and pH_Treatment as columns
pivot_mean_joule_sec <- pivot_wider(mean_joule_sec, names_from = pH_Treatment, values_from = Mean_joule_sec)

# Calculate the percent difference
difference_mean_joule_sec <- pivot_mean_joule_sec %>%
  group_by(Temp_Treatment) %>%
  mutate(Percent_Difference = (Ambient-Low)) %>% 
   mutate(Percent_Difference = Percent_Difference/Low * 100) %>% 
  mutate(Percent_Difference=paste0(Percent_Difference,"%"))

# Rename columns
colnames(difference_mean_joule_sec) <- c("Temperature Treatment", "Ambient Energy Expenditure (J/h)", "Low Energy Expenditure (J/h)", "Percent Difference")

#  "Low" has a lower value than "Ambient," and the difference is expressed as a negative percentage of how much lower "Low" is compared to "Ambient." (this is without weight normalization)


# Print the resulting data frame
print(difference_mean_joule_sec)

# Export the table
write.csv(difference_mean_joule_sec, "percent_difference_table.csv", row.names = FALSE)
```

```{r}

experiment.data <- read_csv(here("Data", "Mesocosm_Data", "Completed_Mesocosm_Dataset_TA_pH.csv")) %>% 
  mutate(Temp_Treatment = as.factor(Temp_Treatment),
         pH_Treatment = as.factor(pH_Treatment)) %>% 
  filter(pH_Treatment != "Sump")

joule.rates.dataset <- left_join(experiment.data, joule.rates.dataset, by = c("Temp_Treatment", "pH_Treatment"))

#load in the data set and select for temperature, rate, and pH treatment
joule.rates.tpc <- joule.rates.dataset %>% 
  mutate(rate=J.hr.per.snail, temp=Temp.C, temp2=Temp_C) %>%
  dplyr::select(Temp_Treatment, pH_Treatment, temp, rate) 

# Create a single ggplot graph with both curves
joule.rates.plot.1 <- ggplot(joule.rates.tpc, aes(temp, rate, color = pH_Treatment)) +
  geom_image(aes(image = image), size = 0.075) +
  theme_bw(base_size = 12) +
  labs(
    x = 'Temperature (ºC)',
    y = 'Joule/Sec',
    title = 'Energetic Expenditure Across Temperatures (~7.9 and ~7.7 pH)'
  ) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"))

# Create a single ggplot graph with both curves
joule.rates.plot.2 <- ggplot(joule.rates.tpc, aes(temp2, rate, color = pH_Treatment)) +
  geom_image(aes(image = image), size = 0.075) +
  theme_bw(base_size = 12) +
  labs(
    x = 'Temperature (ºC)',
    y = 'Joule/Sec',
    title = 'Energetic Expenditure Across Temperatures Experimental Temp (~7.9 and ~7.7 pH)'
  ) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"))

# Print the combined plot
print(joule.rates.plot.1)
print(joule.rates.plot.2)

```
```{r}
respo.rates.tpc<- joule.rates.tpc %>% 
  select(temp, rate, pH_Treatment)

# Load in data and filter to keep just a single curve (low pH)
low.pH <- filter(respo.rates.tpc, pH_Treatment == 'Low')

# Load in data and filter to keep just a single curve (high pH)
high.pH <- filter(respo.rates.tpc, pH_Treatment == 'Ambient')

# Sharpe-Schoolfield Thermal Performance Curves

# Get start values and fit model for low pH
start_vals_low <- get_start_vals(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981')

# Fit the Sharpe-Schoolfield model for low pH
sharpe_schoolfield_mod_low <- nls_multstart(
  rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref = 20),
  data = low.pH,
  iter = c(3, 3, 3, 3),
  start_lower = start_vals_low - 10,
  start_upper = start_vals_low + 10,
  lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  supp_errors = 'Y',
  control = nls.lm.control(maxiter=1000),
  convergence_count = FALSE
)

# Look at the model fit summary for low pH
summary(sharpe_schoolfield_mod_low)

# Get predictions for low pH
preds_low <- data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))
preds_low <- broom::augment(sharpe_schoolfield_mod_low, newdata = preds_low)

# Get start values and fit model for high pH
start_vals_high <- get_start_vals(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981')

# Fit the Sharpe-Schoolfield model for high pH
sharpe_schoolfield_mod_high <- nls_multstart(
  rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref = 20),
  data = high.pH,
  iter = c(3, 3, 3, 3),
  start_lower = start_vals_high - 10,
  start_upper = start_vals_high + 10,
  lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  supp_errors = 'Y',
  control = nls.lm.control(maxiter=1000),
  convergence_count = FALSE
)

# Look at the model fit summary for high pH
summary(sharpe_schoolfield_mod_high)

# Get predictions for high pH
preds_high <- data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))
preds_high <- broom::augment(sharpe_schoolfield_mod_high, newdata = preds_high)

# Combine low pH and high pH predictions
combined_preds <- rbind(
  cbind(preds_low, pH_Treatment = 'Low'),
  cbind(preds_high, pH_Treatment = 'Ambient')
)

# Plot the results for both low pH and high pH
ggplot(combined_preds) +
  geom_image(aes(temp, rate, image=image, color = pH_Treatment),
             respo.rates.tpc, size = 0.075, alpha = 0.5) +
  geom_line(aes(temp, .fitted, color = pH_Treatment)) +
  theme_bw() +
  labs(
    x = 'Temperature',
    y = 'Rate',
    title = 'Sharpe-Schoolfield Model Fit for TPC Curves Low (~7.7) and Ambient (8.0) pH'
  ) +
  scale_color_manual(values = c('Low' = 'cyan3', 'Ambient' = 'orange'))

```


```{r}
# Bootstrapping Sharpe Schoolfield

sharpeshool_low_pH_fit <- nest(low.pH, data = c(temp, rate)) %>%
  mutate(sharpeschoolhigh = map(data, ~nls.multstart::nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 20),
                        data = .x,
                        iter = 500,
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(sharpeschoolhigh, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
low_pH_preds <- select(sharpeshool_low_pH_fit, preds) %>%
  unnest(preds)

# Bootstrap models  Refit model using nlsLM
sharpeschool_low_fit_nlsLM <- minpack.lm::nlsLM(rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref=20),
                                   data = low.pH,
                                   start = coef(sharpeshool_low_pH_fit$sharpeschoolhigh[[1]]),
                                   lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                   upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                   control = nls.lm.control(maxiter=1000),
                                   weights = rep(1, nrow(low.pH)))

# Bootstrap using case resampling
boot.low.pH <- Boot(sharpeschool_low_fit_nlsLM, method = 'case')
hist(boot.low.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_low_preds <- boot.low.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref=20))

# Calculate bootstrapped confidence intervals
boot_low_conf_preds <- boot_low_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.low.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_low_conf_preds, fill = 'cyan3', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Energetic Expenditure (J/h)',
       title = 'Respiration Rate for *Tegula funebralis* at Low pH (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.low.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_line(aes(temp, pred, group = iter), data = boot_low_preds, col = 'cyan3', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate for *Tegula funebralis* at Low pH (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

sharpeshool_high_pH_fit <- nest(high.pH, data = c(temp, rate)) %>%
  mutate(sharpeschoolhigh = map(data, ~nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 20),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(sharpeschoolhigh, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
high_pH_preds <- select(sharpeshool_high_pH_fit, preds) %>%
  unnest(preds)

# Refit model using nlsLM for high pH
sharpeschool_high_fit_nlsLM <- minpack.lm::nlsLM(rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref=20),
                                    data = high.pH,
                                    start = coef(sharpeshool_high_pH_fit$sharpeschoolhigh[[1]]),
                                    lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                    upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                    control = nls.lm.control(maxiter=1000),
                                    weights = rep(1, nrow(high.pH)))

# Bootstrap using case resampling
boot.high.pH <- Boot(sharpeschool_high_fit_nlsLM, method = 'case')
hist(boot.high.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_high_preds <- boot.high.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref=20))

# Calculate bootstrapped confidence intervals
boot_high_conf_preds <- boot_high_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.high.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_high_conf_preds, fill = 'orange', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Energetic Expenditure (J/h)',
       title = 'Respiration Rate for *Tegula funebralis* at Ambient pH (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.high.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_line(aes(temp, pred, group = iter), data = boot_high_preds, col = 'orange', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate for *Tegula funebralis* at Ambient pH (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 149, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Combine the plots
boot.low.pH.plot + boot.low.pH.plot.predictions

# Combine the plots
boot.high.pH.plot + boot.high.pH.plot.predictions


boot.low.pH.predictions + boot.low.pH.plot.predictions
```

```{r}

joule.rates.tpc<- joule.rates.tpc %>% 
  select(temp, rate, Temp_Treatment, pH_Treatment)

# fit every model formulation in rTPC
model_selection_fits <- nest(joule.rates.tpc, data = c(temp, rate)) %>% 
   mutate(boatman = map(data, ~nls_multstart(rate~boatman_2017(temp = temp, rmax, tmin, tmax, a,b),
                        data = .x,
                        iter = c(4,4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'boatman_2017') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'boatman_2017') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'boatman_2017'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'boatman_2017'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         gaussian = map(data, ~nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         oneill = map(data, ~nls_multstart(rate~oneill_1972(temp = temp, rmax, ctmax, topt, q10),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'oneill_1972') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'oneill_1972') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'oneill_1972'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'oneill_1972'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         quadratic = map(data, ~nls_multstart(rate~quadratic_2008(temp = temp, a, b, c),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'quadratic_2008') - 0.5,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'quadratic_2008') + 0.5,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'quadratic_2008'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'quadratic_2008'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         rezende = map(data, ~nls_multstart(rate~rezende_2019(temp = temp, q10, a,b,c),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'rezende_2019') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'rezende_2019') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'rezende_2019'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'rezende_2019'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         sharpeschoolfull = map(data, ~nls_multstart(rate~sharpeschoolfull_1981(temp = temp, r_tref,e,el,tl,eh,th, tref = 15),
                        data = .x,
                        iter = c(4,4,4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         sharpeschoolhigh = map(data, ~nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 15),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         weibull = map(data, ~nls_multstart(rate~weibull_1995(temp = temp, a,topt,b,c),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'weibull_1995') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'weibull_1995') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'weibull_1995'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'weibull_1995'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)))

glimpse(select(model_selection_fits, 1:10))

# stack models
model_stack <- select(model_selection_fits, -data) %>%
  pivot_longer(., names_to = 'model_name', values_to = 'fit', boatman:weibull)

# get parameters using tidy
params <- model_stack %>%
  mutate(., est = map(fit, tidy)) %>%
  select(-fit) %>%
  unnest(est)

# get predictions using augment
newdata <- tibble(temp = seq(min(respo.rates.tpc$temp), max(respo.rates.tpc$temp), length.out = 100))
model_preds <- model_stack %>%
  mutate(., preds = map(fit, augment, newdata = newdata)) %>%
  select(-fit) %>%
  unnest(preds)

# seperating the curves for graphing seperate
high_pH <- filter(respo.rates.tpc, pH_Treatment == "Ambient") 
high_pH_model_preds <- filter(model_preds, pH_Treatment == "Ambient")
low_pH <- filter(respo.rates.tpc, pH_Treatment == "Low") 
low_pH_model_preds <- filter(model_preds, pH_Treatment == "Low")

# take a random point from each model for labelling
high_pH_model_labs <- filter(high_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()

# take a random point from each model for labelling
low_pH_model_labs <- filter(low_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()


# plot
ggplot(model_preds, aes(temp, rate, color = pH_Treatment)) +
  geom_point(aes(temp, rate), respo.rates.tpc) +
  geom_line(aes(temp, .fitted)) +
  facet_wrap(~model_name, labeller = labeller(model_name = label_facets_num),
             scales = 'free', ncol = 5) +
  theme_minimal(base_size = 12) +
  theme(legend.position = 'none',
        strip.text = element_text(hjust = 0),
        strip.background = element_blank()) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"), 
                     name = "Treatment") +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic Rate',
       title = 'Fits of TPC Models') +
  geom_hline(aes(yintercept = 0), linetype = 2)

# multiple models low pH plot
ggplot(low_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', low_pH_model_labs) +
  geom_point(aes(temp, rate), low_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - low pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)

# multiple models high pH plot
ggplot(high_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', high_pH_model_labs) +
  geom_point(aes(temp, rate), high_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - high pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)

glimpse(select(model_selection_fits, 1:10))

# stack models
model_stack <- select(model_selection_fits, -data) %>%
  pivot_longer(., names_to = 'model_name', values_to = 'fit', boatman:weibull)

# get parameters using tidy
params <- model_stack %>%
  mutate(., est = map(fit, tidy)) %>%
  select(-fit) %>%
  unnest(est)

# get predictions using augment
newdata <- tibble(temp = seq(min(respo.rates.tpc$temp), max(respo.rates.tpc$temp), length.out = 100))
model_preds <- model_stack %>%
  mutate(., preds = map(fit, augment, newdata = newdata)) %>%
  select(-fit) %>%
  unnest(preds)

# seperating the curves for graphing seperate
high_pH <- filter(respo.rates.tpc, pH_Treatment == "Ambient") 
high_pH_model_preds <- filter(model_preds, pH_Treatment == "Ambient")
low_pH <- filter(respo.rates.tpc, pH_Treatment == "Low") 
low_pH_model_preds <- filter(model_preds, pH_Treatment == "Low")

# take a random point from each model for labelling
high_pH_model_labs <- filter(high_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()

# take a random point from each model for labelling
low_pH_model_labs <- filter(low_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()


# plot
ggplot(model_preds, aes(temp, rate, color = pH_Treatment)) +
  geom_point(aes(temp, rate), respo.rates.tpc) +
  geom_line(aes(temp, .fitted)) +
  facet_wrap(~model_name, labeller = labeller(model_name = label_facets_num),
             scales = 'free', ncol = 5) +
  theme_minimal(base_size = 12) +
  theme(legend.position = 'none',
        strip.text = element_text(hjust = 0),
        strip.background = element_blank()) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"), 
                     name = "Treatment") +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic Rate',
       title = 'Fits of TPC Models') +
  geom_hline(aes(yintercept = 0), linetype = 2)

# multiple models low pH plot
ggplot(low_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', low_pH_model_labs) +
  geom_point(aes(temp, rate), low_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - low pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)

# multiple models high pH plot
ggplot(high_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', high_pH_model_labs) +
  geom_point(aes(temp, rate), high_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - high pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)
```



# Respiration Summary Statistics 

```{r Respiration Summary Statistics}

respo.rates.dataset <- read_csv(here("Data", "Thinned_Respirometry_Data", "Respiration.Rates.Dataset.csv"))

#creating a function for standard error 
se <- function(x) (sd(x) / sqrt(length(x)))

respo.rates.stats <- respo.rates.dataset %>% 
  dplyr::select(Snail_ID, Temp_Treatment, pH_Treatment, 
         umolO2.gram.hr.corrected, umolO2.gram.hr.uncorrected, Temp.C) %>%
  mutate(pH_Treatment = as.factor(pH_Treatment)) %>% 
  group_by(Temp_Treatment, pH_Treatment) %>% 
  summarize(mean.umolO2.gram.hr.corrected =mean(umolO2.gram.hr.corrected),
            var.umolO2.gram.hr.corrected = var(umolO2.gram.hr.corrected),
            sd.umolO2.gram.hr.corrected = sd(umolO2.gram.hr.corrected),
            se.umolO2.gram.hr.corrected =se(umolO2.gram.hr.corrected),
            mean.umolO2.gram.hr.uncorrected = mean(umolO2.gram.hr.uncorrected),
            var.umolO2.gram.hr.uncorrected = var(umolO2.gram.hr.uncorrected),
            sd.umolO2.gram.hr.uncorrected = sd(umolO2.gram.hr.uncorrected),
            se.umolO2.gram.hr.uncorrected =se(umolO2.gram.hr.uncorrected),
            mean.Temp.C = mean(Temp.C),
            var.Temp.C = var(Temp.C),
            sd.Temp.C = sd(Temp.C),
            se.Temp.C = se(Temp.C))

as_tibble(respo.rates.stats)
```
#Cleaning and Visualzing Data for Thermal Performance Curve Model Selection

```{r Cleaning and Visualizing Respo Data for rTPC Model Selection}

#load in the data set and select for temperature, rate, and pH treatment
respo.rates.tpc <- respo.rates.dataset %>% 
  mutate(rate=umolO2.gram.hr.corrected, temp=Temp.C) %>%
  dplyr::select(pH_Treatment, temp, rate)

# Create a single ggplot graph with both curves and label the key as "Treatment"
combined_plot <- ggplot(respo.rates.tpc, aes(temp, rate, color = pH_Treatment)) +
  geom_image(aes(image = image), size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(
    x = 'Temperature (ºC)',
    y = 'Respiration Rate' ) +
  facet_wrap(~pH_Treatment) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"), 
                     name = "Treatment") +
  theme_minimal()

# Print the combined plot
print(combined_plot)

```



```{r}

# fit every model formulation in rTPC
model_selection_fits <- nest(respo.rates.tpc, data = c(temp, rate)) %>% 
   mutate(boatman = map(data, ~nls_multstart(rate~boatman_2017(temp = temp, rmax, tmin, tmax, a,b),
                        data = .x,
                        iter = c(4,4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'boatman_2017') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'boatman_2017') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'boatman_2017'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'boatman_2017'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         gaussian = map(data, ~nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         oneill = map(data, ~nls_multstart(rate~oneill_1972(temp = temp, rmax, ctmax, topt, q10),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'oneill_1972') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'oneill_1972') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'oneill_1972'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'oneill_1972'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         quadratic = map(data, ~nls_multstart(rate~quadratic_2008(temp = temp, a, b, c),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'quadratic_2008') - 0.5,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'quadratic_2008') + 0.5,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'quadratic_2008'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'quadratic_2008'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         rezende = map(data, ~nls_multstart(rate~rezende_2019(temp = temp, q10, a,b,c),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'rezende_2019') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'rezende_2019') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'rezende_2019'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'rezende_2019'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         sharpeschoolfull = map(data, ~nls_multstart(rate~sharpeschoolfull_1981(temp = temp, r_tref,e,el,tl,eh,th, tref = 15),
                        data = .x,
                        iter = c(4,4,4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolfull_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         sharpeschoolhigh = map(data, ~nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 15),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         weibull = map(data, ~nls_multstart(rate~weibull_1995(temp = temp, a,topt,b,c),
                        data = .x,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'weibull_1995') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'weibull_1995') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'weibull_1995'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'weibull_1995'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)))

glimpse(select(model_selection_fits, 1:10))

# stack models
model_stack <- select(model_selection_fits, -data) %>%
  pivot_longer(., names_to = 'model_name', values_to = 'fit', boatman:weibull)

# get parameters using tidy
params <- model_stack %>%
  mutate(., est = map(fit, tidy)) %>%
  select(-fit) %>%
  unnest(est)

# get predictions using augment
newdata <- tibble(temp = seq(min(respo.rates.tpc$temp), max(respo.rates.tpc$temp), length.out = 100))
model_preds <- model_stack %>%
  mutate(., preds = map(fit, augment, newdata = newdata)) %>%
  select(-fit) %>%
  unnest(preds)

# seperating the curves for graphing seperate
high_pH <- filter(respo.rates.tpc, pH_Treatment == "Ambient") 
high_pH_model_preds <- filter(model_preds, pH_Treatment == "Ambient")
low_pH <- filter(respo.rates.tpc, pH_Treatment == "Low") 
low_pH_model_preds <- filter(model_preds, pH_Treatment == "Low")

# take a random point from each model for labelling
high_pH_model_labs <- filter(high_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()

# take a random point from each model for labelling
low_pH_model_labs <- filter(low_pH_model_preds, temp < 24) %>%
  group_by(., model_name) %>%
  sample_n(., 1) %>%
  ungroup()


# plot
ggplot(model_preds, aes(temp, rate, color = pH_Treatment)) +
  geom_point(aes(temp, rate), respo.rates.tpc) +
  geom_line(aes(temp, .fitted)) +
  facet_wrap(~model_name, labeller = labeller(model_name = label_facets_num),
             scales = 'free', ncol = 5) +
  theme_minimal(base_size = 12) +
  theme(legend.position = 'none',
        strip.text = element_text(hjust = 0),
        strip.background = element_blank()) +
  scale_color_manual(values = c("Low" = "cyan3", "Ambient" = "orange"), 
                     name = "Treatment") +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic Rate',
       title = 'Fits of TPC Models') +
  geom_hline(aes(yintercept = 0), linetype = 2)

# multiple models low pH plot
ggplot(low_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', low_pH_model_labs) +
  geom_point(aes(temp, rate), low_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - low pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)

# multiple models high pH plot
ggplot(high_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(col = model_name)) +
  geom_label_repel(aes(temp, .fitted, label = model_name, col = model_name), fill = 'white', nudge_y = 2, segment.size = 0.5, segment.colour = 'grey50', high_pH_model_labs) +
  geom_point(aes(temp, rate), high_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Model Fits - high pH') +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  scale_color_brewer(type = 'qual', palette = 2)

```

# Thermal Performance Curve Model Selection 

```{r}

model_aic <- model_stack %>%
  mutate(., info = map(fit, glance),
         AICc =  map_dbl(fit, MuMIn::AICc)) %>%
  select(-fit) %>%
  unnest(info) %>%
  select(Treatment=pH_Treatment, model_name, sigma, AIC, AICc, BIC, df.residual)

print(model_aic)

# Find the best model across both pH_Treatment levels
best_model <- model_aic %>%
  group_by(Treatment) %>% 
  filter(AICc == min(AICc)) %>%
  pull(model_name, Treatment)

# Print the best model
print(best_model)

# showing data in table format
model_aic %>% 
  group_by(model_name) %>% 
  gt(rowname_col = "pH_Treatment") %>%
  tab_header(title = md("**Thermal Performance Models Statistical Summaries**")) %>% 
  gt_highlight_rows(rows = c(7,10), font_weight = "normal") 

low_pH_best_model <- model_aic %>%
  filter(Treatment == "Low") %>% 
  filter(AICc == min(AICc)) %>%
  pull(model_name)

high_pH_best_model <- model_aic %>%
  filter(Treatment == "Ambient") %>% 
  filter(AICc == min(AICc)) %>%
  pull(model_name)

# get colour code
col_best_mod = RColorBrewer::brewer.pal(n = 6, name = "Dark2")[6]

# multiple models low pH plot (best fit curve)
ggplot(low_pH_model_preds, aes(temp, .fitted)) +
  geom_line(aes(group = model_name), col = 'grey50', alpha = 0.5) +
  geom_line(data = filter(low_pH_model_preds, model_name==low_pH_best_model), col = col_best_mod) +
  geom_label_repel(aes(temp, .fitted, label = model_name), fill = 'white', nudge_y = 0.8, segment.size = 0.2, segment.colour = 'grey50', data = filter(low_pH_model_labs, model_name == low_pH_best_model), col = col_best_mod) +
  geom_point(aes(temp, rate), low_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Best Fit Model - low pH') +
  geom_hline(aes(yintercept = 0), linetype = 2)

# multiple models high pH plot
ggplot(high_pH_model_preds, aes(temp, .fitted, color = pH_Treatment)) +
  geom_line(aes(group = model_name), col = 'grey50', alpha = 0.5) +
  geom_line(data = filter(high_pH_model_preds, model_name==high_pH_best_model), col = col_best_mod) +
  geom_label_repel(aes(temp, .fitted, label = model_name), fill = 'white', nudge_y = 0.8, segment.size = 0.2, segment.colour = 'grey50', data = filter(high_pH_model_labs, model_name == high_pH_best_model), col = col_best_mod) +
  geom_point(aes(temp, rate), high_pH) +
  theme_bw(base_size = 12) +
  theme(legend.position = 'none') +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'rTPC Best Fit Model - high pH') +
  geom_hline(aes(yintercept = 0), linetype = 2)



```

Choose the Sharpe Schoolfield model(high) because it had the lowest AIC values for 7.7 and 8.0 pH, collectively and was a biological model used for ectotherms that fit the curve correctly. 


#Respiration Thermal Performance Curves

```{r}
respo.rates.dataset <- joules.respo.rates.dataset

#load in the data set and select for temperature, rate, and pH treatment
respo.rates.tpc <- respo.rates.dataset %>% 
  mutate(rate=umolO2.gram.hr.corrected, temp=Temp.C) %>%
  dplyr::select(pH_Treatment, temp, rate)

# Load in data and filter to keep just a single curve (low pH)
low.pH <- filter(respo.rates.tpc, pH_Treatment == 'Low') 

# Load in data and filter to keep just a single curve (high pH)
high.pH <- filter(respo.rates.tpc, pH_Treatment == 'Ambient') 

# Gaussian Thermal Performance Curves

# Get start values and fit model for low pH
start_vals_low <- get_start_vals(low.pH$temp, low.pH$rate, model_name = 'gaussian_1987')

# Fit the Gaussian model for low pH
gaussian_mod_low <- nls_multstart(
  rate ~ gaussian_1987(temp = temp, rmax, topt, a),
  data = low.pH,
  iter = c(4, 4, 4),
  start_lower = start_vals_low - 10,
  start_upper = start_vals_low + 10,
  lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'gaussian_1987'),
  upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'gaussian_1987'),
  supp_errors = 'Y',
  convergence_count = FALSE
)

# Look at the model fit summary for low pH
summary(gaussian_mod_low)

# Get predictions for low pH
preds_low <- data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))
preds_low <- broom::augment(gaussian_mod_low, newdata = preds_low)

# Get start values and fit model for high pH
start_vals_high <- get_start_vals(high.pH$temp, high.pH$rate, model_name = 'gaussian_1987')

# Fit the Gaussian model for high pH
gaussian_mod_high <- nls_multstart(
  rate ~ gaussian_1987(temp = temp, rmax, topt, a),
  data = high.pH,
  iter = c(4, 4, 4),
  start_lower = start_vals_high - 10,
  start_upper = start_vals_high + 10,
  lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'gaussian_1987'),
  upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'gaussian_1987'),
  supp_errors = 'Y',
  convergence_count = FALSE
)

# Look at the model fit summary for high pH
summary(gaussian_mod_high)

# Get predictions for high pH
preds_high <- data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))
preds_high <- broom::augment(gaussian_mod_high, newdata = preds_high)

# Combine low pH and high pH predictions
combined_preds <- rbind(
  cbind(preds_low, pH_Treatment = 'Low'),
  cbind(preds_high, pH_Treatment = 'Ambient')
)

# Plot the results for both low pH and high pH
ggplot(combined_preds) +
  geom_image(aes(temp, rate, image=image, color = pH_Treatment),
             respo.rates.tpc, size = 0.075, alpha = 0.5) +
  geom_line(aes(temp, .fitted, color = pH_Treatment)) +
  theme_bw() +
  labs(
    x = 'Temperature',
    y = 'Rate',
    title = 'Gaussian Model Fit for TPC Curves - Low and High pH'
  ) +
  scale_color_manual(values = c('Low' = 'cyan3', 'Ambient' = 'orange'))

# Bootstrapping Gaussian 
gaussian_low_pH_fit <- nest(low.pH, data = c(temp, rate)) %>%
  mutate(gaussian = map(data, ~nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(gaussian, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
low_pH_preds <- select(gaussian_low_pH_fit, preds) %>%
  unnest(preds)

# Bootstrap models  Refit model using nlsLM
gaussian_low_fit_nlsLM <- minpack.lm::nlsLM(rate ~ gaussian_1987(temp = temp, rmax, topt, a),
                                   data = low.pH,
                                   start = coef(gaussian_low_pH_fit$gaussian[[1]]),
                                   lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'gaussian_1987'),
                                   upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'gaussian_1987'),
                                   control = nls.lm.control(maxiter = 200), 
                                   weights = rep(1, nrow(low.pH)))

# Bootstrap using case resampling
boot.low.pH <- Boot(gaussian_low_fit_nlsLM, method = 'case')
hist(boot.low.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_low_pH_preds <- boot.low.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = temp, rmax, topt, a))

# Calculate bootstrapped confidence intervals
boot_low_conf_preds <- boot_low_pH_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.low.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_low_conf_preds, fill = 'cyan3', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.low.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_line(aes(temp, pred, group = iter), data = boot_low_pH_preds, col = 'cyan3', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

boot.low.pH.plot + boot.low.pH.plot.predictions

gaussian_high_pH_fit <- nest(high.pH, data = c(temp, rate)) %>%
  mutate(gaussian = map(data, ~nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a),
                        data = .x,
                        iter = c(4,4,4),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(gaussian, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
high_pH_preds <- select(gaussian_high_pH_fit, preds) %>%
  unnest(preds)

# Bootstrap models  Refit model using nlsLM
gaussian_high_fit_nlsLM <- minpack.lm::nlsLM(rate ~ gaussian_1987(temp = temp, rmax, topt, a),
                                   data = high.pH,
                                   start = coef(gaussian_high_pH_fit$gaussian[[1]]),
                                   lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'gaussian_1987'),
                                   upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'gaussian_1987'),
                                   control = nls.lm.control(maxiter = 200), 
                                   weights = rep(1, nrow(high.pH)))

# Bootstrap using case resampling
boot.high.pH <- Boot(gaussian_high_fit_nlsLM, method = 'case')
hist(boot.high.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_high_pH_preds <- boot.high.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = temp, rmax, topt, a))

# Calculate bootstrapped confidence intervals
boot_high_conf_preds <- boot_high_pH_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.high.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_high_conf_preds, fill = 'orange', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.high.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_line(aes(temp, pred, group = iter), data = boot_high_pH_preds, col = 'orange', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

boot.high.pH.plot + boot.high.pH.plot.predictions

```


```{r}

# get parameters of fitted model
gaussian_high_parameters <- broom::tidy(gaussian_high_fit_nlsLM) %>%
  select(param = term, estimate)

# calculate confidence intervals of models

# asymptotic confidence intervals estimate
ci_gaussian_high_parameters_1 <- nlstools::confint2(gaussian_high_fit_nlsLM, method = 'asymptotic') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'asymptotic')

# profile likelihood confidence intervals estimate
ci_gaussian_high_parameters_2 <- confint(gaussian_high_fit_nlsLM) %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'profile')

# CIs from case resampling
ci_gaussian_high_parameters_3 <- confint(gaussian_high_fit_nlsLM, method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

# CIs from residual resampling
ci_gaussian_high_parameters_4 <- Boot(gaussian_high_fit_nlsLM, method = 'residual') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'residual bootstrap')

ci_gaussian_high_parameters <- bind_rows(ci_gaussian_high_parameters_1, ci_gaussian_high_parameters_2, ci_gaussian_high_parameters_3, ci_gaussian_high_parameters_4) %>%
  left_join(., gaussian_high_parameters) %>% 
  mutate(Treatment="Ambient")

# get parameters of fitted model
gaussian_low_parameters <- broom::tidy(gaussian_low_fit_nlsLM) %>%
  select(param = term, estimate)

# calculate confidence intervals of models

# asymptotic confidence intervals estimate
ci_gaussian_low_parameters_1 <- nlstools::confint2(gaussian_low_fit_nlsLM, method = 'asymptotic') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'asymptotic')

# profile likelihood confidence intervals estimate
ci_gaussian_low_parameters_2 <- confint(gaussian_low_fit_nlsLM) %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'profile')

# CIs from case resampling
ci_gaussian_low_parameters_3 <- confint(gaussian_low_fit_nlsLM, method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

# CIs from residual resampling
ci_gaussian_low_parameters_4 <- Boot(gaussian_low_fit_nlsLM, method = 'residual') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'residual bootstrap')

ci_gaussian_low_parameters <- bind_rows(ci_gaussian_low_parameters_1, ci_gaussian_low_parameters_2, ci_gaussian_low_parameters_3, ci_gaussian_low_parameters_4) %>%
  left_join(., gaussian_low_parameters) %>% 
  mutate(Treatment="Low")

# CI gaussian low ggplot plot 
ggplot(ci_gaussian_low_parameters, aes(forcats::fct_relevel(method, c('profile', 'asymptotic')), estimate, col = method)) +
  geom_hline(aes(yintercept = conf_lower), linetype = 2, filter(ci_gaussian_low_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper), linetype = 2, filter(ci_gaussian_low_parameters, method == 'profile')) +
  geom_point(size = 4) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(title = 'Calculation of Confidence Intervals for Model Parameters', y = 'Estimate', color = 'Method') +
  theme(axis.text.x = element_text(size = 6, hjust = 0.5), plot.title = element_text(hjust = 0.5))

# CI gaussian high ggplot plot
ggplot(ci_gaussian_high_parameters, aes(forcats::fct_relevel(method, c('profile', 'asymptotic')), estimate, col = method)) +
  geom_hline(aes(yintercept = conf_lower), linetype = 2, filter(ci_gaussian_high_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper), linetype = 2, filter(ci_gaussian_high_parameters, method == 'profile')) +
  geom_point(size = 4) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(title = 'Calculation of Confidence Intervals for Model Parameters', y = 'Estimate', color = 'Method') +
  theme(axis.text.x = element_text(size = 6, hjust = 0.5), plot.title = element_text(hjust = 0.5))

#Presenting TPC parameter data as a table 
tpc_parameters <- full_join(ci_gaussian_high_parameters, ci_gaussian_low_parameters) 
as_tibble(tpc_parameters)

# Create the plot
ggplot(tpc_parameters, aes(x = method, y = estimate, ymin = conf_lower, ymax = conf_upper, color = Treatment)) +
  geom_hline(aes(yintercept = conf_lower, color = Treatment), alpha= 0.3, linetype = 2, filter(tpc_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper, color = Treatment), alpha= 0.3, linetype = 2, filter(tpc_parameters, method == 'profile')) +
  geom_point(size = 4, position = position_dodge(width = 1)) +  # Adjust dodge.width as needed
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper), position = position_dodge(width = 1)) +
  theme_minimal() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(
    title = "Calculation of Confidence Intervals for Model Parameters",
    y = "Estimate",
    color = "Treatment") +
  scale_color_manual(values = c("cyan3", "orange")) +
    theme(
    axis.title.y = element_text(size = 6),
    axis.text.x = element_text(size = 6),  # Adjust the size of the x-axis labels
    axis.text.y = element_text(size = 6),  # Adjust the size of the y-axis labels
    strip.text = element_text(size = 10, face = "bold"),  # Bold facet wrap headers
    legend.text = element_text(size = 6),  # Adjust the size of legend text
    legend.title = element_text(size = 8, face = "bold"))  # Bold legend title

#Extracting Extra TPC parameters 
high_extra_params <- calc_params(gaussian_high_fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

high_ci_extra_params <- Boot(gaussian_high_fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(gaussian_high_fit_nlsLM)), R = 1000, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

high_pH_ci_extra_params <- left_join(high_ci_extra_params, high_extra_params)
high_pH_TPC_parameters <- as_tibble(high_pH_ci_extra_params)%>% 
  mutate(Treatment="Ambient")

low_extra_params <- calc_params(gaussian_low_fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

low_ci_extra_params <- Boot(gaussian_low_fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(gaussian_low_fit_nlsLM)), R = 1000, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')
  
low_pH_ci_extra_params <- left_join(low_ci_extra_params, low_extra_params)
low_pH_TPC_parameters <- as_tibble(low_pH_ci_extra_params) %>% 
  mutate(Treatment="Low")

#Presenting TPC parameter data as a table 
TPC_parameters <- full_join(high_pH_TPC_parameters, low_pH_TPC_parameters) 
as_tibble(TPC_parameters)
  
TPC_parameters %>% pivot_wider(names_from=Treatment, values_from=c(conf_lower, conf_upper, estimate))

# TPC parameters plot
ggplot(TPC_parameters, aes(forcats::fct_relevel(Treatment), estimate, color = Treatment)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  geom_hline(aes(yintercept = conf_lower, color = Treatment), alpha= 0.3, linetype = 2,
             filter(TPC_parameters, method == 'case bootstrap')) +
  geom_hline(aes(yintercept = conf_upper, color = Treatment), alpha= 0.3, linetype = 2,
             filter(TPC_parameters, method == 'case bootstrap')) +
  theme_minimal(base_size = 12) +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 5)) +
  labs( title = "Calculation of Confidence Intervals for Model Parameters",
        x = 'Treatment', y = 'Estimate', color = 'Treatment') +
  scale_color_manual(values = c("orange", "cyan3")) +  # Set colors as orange and blue
    theme(
    axis.title.y = element_text(size = 8),
    axis.text.x = element_text(size = 8),  # Adjust the size of the x-axis labels
    axis.text.y = element_text(size = 8),  # Adjust the size of the y-axis labels
    strip.text = element_text(size = 8, face = "bold"),  # Bold facet wrap headers
    legend.text = element_text(size = 8),  # Adjust the size of legend text
    legend.title = element_text(size = 8, face = "bold"))  # Bold legend title


```



# Sharpe School Field Thermal Performance Curve

```{r}
# Load in data and filter to keep just a single curve (low pH)
low.pH <- filter(respo.rates.tpc, pH_Treatment == 'Low')

# Load in data and filter to keep just a single curve (high pH)
high.pH <- filter(respo.rates.tpc, pH_Treatment == 'Ambient')

# Sharpe-Schoolfield Thermal Performance Curves

# Get start values and fit model for low pH
start_vals_low <- get_start_vals(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981')

# Fit the Sharpe-Schoolfield model for low pH
sharpe_schoolfield_mod_low <- nls_multstart(
  rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref = 20),
  data = low.pH,
  iter = c(3, 3, 3, 3),
  start_lower = start_vals_low - 10,
  start_upper = start_vals_low + 10,
  lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  supp_errors = 'Y',
  control = nls.lm.control(maxiter=1000),
  convergence_count = FALSE
)

# Look at the model fit summary for low pH
summary(sharpe_schoolfield_mod_low)

# Get predictions for low pH
preds_low <- data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))
preds_low <- broom::augment(sharpe_schoolfield_mod_low, newdata = preds_low)

# Get start values and fit model for high pH
start_vals_high <- get_start_vals(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981')

# Fit the Sharpe-Schoolfield model for high pH
sharpe_schoolfield_mod_high <- nls_multstart(
  rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref = 20),
  data = high.pH,
  iter = c(3, 3, 3, 3),
  start_lower = start_vals_high - 10,
  start_upper = start_vals_high + 10,
  lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
  supp_errors = 'Y',
  control = nls.lm.control(maxiter=1000),
  convergence_count = FALSE
)

# Look at the model fit summary for high pH
summary(sharpe_schoolfield_mod_high)

# Get predictions for high pH
preds_high <- data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))
preds_high <- broom::augment(sharpe_schoolfield_mod_high, newdata = preds_high)

# Combine low pH and high pH predictions
combined_preds <- rbind(
  cbind(preds_low, pH_Treatment = 'Low'),
  cbind(preds_high, pH_Treatment = 'Ambient')
)

# Plot the results for both low pH and high pH
ggplot(combined_preds) +
  geom_image(aes(temp, rate, image=image, color = pH_Treatment),
             respo.rates.tpc, size = 0.075, alpha = 0.5) +
  geom_line(aes(temp, .fitted, color = pH_Treatment)) +
  theme_bw() +
  labs(
    x = 'Temperature',
    y = 'Rate',
    title = 'Sharpe-Schoolfield Model Fit for TPC Curves Low (~7.7) and Ambient (8.0) pH'
  ) +
  scale_color_manual(values = c('Low' = 'cyan3', 'Ambient' = 'orange'))

# Bootstrapping Sharpe Schoolfield

sharpeshool_low_pH_fit <- nest(low.pH, data = c(temp, rate)) %>%
  mutate(sharpeschoolhigh = map(data, ~nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 20),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(sharpeschoolhigh, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
low_pH_preds <- select(sharpeshool_low_pH_fit, preds) %>%
  unnest(preds)

# Bootstrap models  Refit model using nlsLM
sharpeschool_low_fit_nlsLM <- minpack.lm::nlsLM(rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref=20),
                                   data = low.pH,
                                   start = coef(sharpeshool_low_pH_fit$sharpeschoolhigh[[1]]),
                                   lower = get_lower_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                   upper = get_upper_lims(low.pH$temp, low.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                   control = nls.lm.control(maxiter=1000),
                                   weights = rep(1, nrow(low.pH)))

# Bootstrap using case resampling
boot.low.pH <- Boot(sharpeschool_low_fit_nlsLM, method = 'case')
hist(boot.low.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_low_preds <- boot.low.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(low.pH$temp), max(low.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref=20))

# Calculate bootstrapped confidence intervals
boot_low_conf_preds <- boot_low_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.low.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_low_conf_preds, fill = 'cyan3', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.low.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = low_pH_preds, col = 'cyan3') +
  geom_line(aes(temp, pred, group = iter), data = boot_low_preds, col = 'cyan3', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = low.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate (pH ~7.9)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

sharpeshool_high_pH_fit <- nest(high.pH, data = c(temp, rate)) %>%
  mutate(sharpeschoolhigh = map(data, ~nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 20),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 10,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 10,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         # create new temperature data
         new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 100))),
         # predict over that data,
         preds =  map2(sharpeschoolhigh, new_data, ~augment(.x, newdata = .y)))

# unnest predictions
high_pH_preds <- select(sharpeshool_high_pH_fit, preds) %>%
  unnest(preds)

# Refit model using nlsLM for high pH
sharpeschool_high_fit_nlsLM <- minpack.lm::nlsLM(rate ~ sharpeschoolhigh_1981(temp = temp, r_tref, e, eh, th, tref=20),
                                    data = high.pH,
                                    start = coef(sharpeshool_high_pH_fit$sharpeschoolhigh[[1]]),
                                    lower = get_lower_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                    upper = get_upper_lims(high.pH$temp, high.pH$rate, model_name = 'sharpeschoolhigh_1981'),
                                    control = nls.lm.control(maxiter=1000),
                                    weights = rep(1, nrow(high.pH)))

# Bootstrap using case resampling
boot.high.pH <- Boot(sharpeschool_high_fit_nlsLM, method = 'case')
hist(boot.high.pH, layout = c(2,2))

# Create predictions of each bootstrapped model
boot_high_preds <- boot.high.pH$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = row_number()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(high.pH$temp), max(high.pH$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref=20))

# Calculate bootstrapped confidence intervals
boot_high_conf_preds <- boot_high_preds %>%
  group_by(temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# Plot bootstrapped CIs
boot.high.pH.plot <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), data = boot_high_conf_preds, fill = 'orange', alpha = 0.3) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate',
       title = 'Respiration Rate (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Plot bootstrapped predictions
boot.high.pH.plot.predictions <- ggplot() +
  geom_line(aes(temp, .fitted), data = high_pH_preds, col = 'orange') +
  geom_line(aes(temp, pred, group = iter), data = boot_high_preds, col = 'orange', alpha = 0.007) +
  geom_image(aes(temp, rate, image = image), data = high.pH, size = 0.075, alpha = 0.5) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       title = 'Respiration Rate (pH ~7.7)') +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 20)) +
  scale_x_continuous(limits = c(12, 28), breaks = seq(12, 28, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5))

# Combine the plots
boot.low.pH.plot + boot.low.pH.plot.predictions

# Combine the plots
boot.high.pH.plot + boot.high.pH.plot.predictions

```



```{r}
# get parameters of fitted model
sharpeschool_high_parameters <- broom::tidy(sharpeschool_high_fit_nlsLM) %>%
  select(param = term, estimate)

# calculate confidence intervals of models

# CIs from residual resampling
ci_sharpeschool_high_parameters_1 <- Boot(sharpeschool_high_fit_nlsLM, method = 'residual') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'residual bootstrap')

ci_sharpeschool_high_parameters <- left_join(ci_sharpeschool_high_parameters_1, sharpeschool_high_parameters) %>% 
  mutate(Treatment="Ambient")

# get parameters of fitted model
sharpeschool_low_parameters <- broom::tidy(sharpeschool_low_fit_nlsLM) %>%
  select(param = term, estimate)

# calculate confidence intervals of models

# asymptotic confidence intervals estimate
ci_sharpeschool_low_parameters_1 <- nlstools::confint2(sharpeschool_low_fit_nlsLM, method = 'asymptotic') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'asymptotic')

# profile likelihood confidence intervals estimate
ci_sharpeschool_low_parameters_2 <- confint(sharpeschool_low_fit_nlsLM) %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'profile')

# CIs from case resampling
ci_sharpeschool_low_parameters_3 <- confint(sharpeschool_low_fit_nlsLM, method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

# CIs from residual resampling
ci_sharpeschool_low_parameters_4 <- Boot(sharpeschool_low_fit_nlsLM, method = 'residual') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'residual bootstrap')

ci_sharpeschool_low_parameters <- bind_rows(ci_sharpeschool_low_parameters_1, ci_sharpeschool_low_parameters_2, ci_sharpeschool_low_parameters_3, ci_sharpeschool_low_parameters_4) %>%
  left_join(., sharpeschool_low_parameters) %>% 
  mutate(Treatment="Low")

# CI gaussian low ggplot plot 
ggplot(ci_sharpeschool_low_parameters, aes(forcats::fct_relevel(method, c('profile', 'asymptotic')), estimate, col = method)) +
  geom_hline(aes(yintercept = conf_lower), linetype = 2, filter(ci_sharpeschool_low_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper), linetype = 2, filter(ci_sharpeschool_low_parameters, method == 'profile')) +
  geom_point(size = 4) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(title = 'Calculation of Confidence Intervals for Model Parameters', y = 'Estimate', color = 'Method') +
  theme(axis.text.x = element_text(size = 6, hjust = 0.5), plot.title = element_text(hjust = 0.5))

# CI gaussian high ggplot plot
ggplot(ci_sharpeschool_high_parameters, aes(forcats::fct_relevel(method, c('profile', 'asymptotic')), estimate, col = method)) +
  geom_hline(aes(yintercept = conf_lower), linetype = 2, filter(ci_sharpeschool_high_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper), linetype = 2, filter(ci_sharpeschool_high_parameters, method == 'profile')) +
  geom_point(size = 4) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(title = 'Calculation of Confidence Intervals for Model Parameters', y = 'Estimate', color = 'Method') +
  theme(axis.text.x = element_text(size = 6, hjust = 0.5), plot.title = element_text(hjust = 0.5))

#Presenting TPC parameter data as a table 
sharpeschool_tpc_parameters <- full_join(ci_sharpeschool_high_parameters, ci_sharpeschool_low_parameters) 
as_tibble(sharpeschool_tpc_parameters)

# Create the plot
ggplot(sharpeschool_tpc_parameters, aes(x = method, y = estimate, ymin = conf_lower, ymax = conf_upper, color = Treatment)) +
  geom_hline(aes(yintercept = conf_lower, color = Treatment), alpha= 0.3, linetype = 2, filter(sharpeschool_tpc_parameters, method == 'profile')) +
  geom_hline(aes(yintercept = conf_upper, color = Treatment), alpha= 0.3, linetype = 2, filter(sharpeschool_tpc_parameters, method == 'profile')) +
  geom_point(size = 4, position = position_dodge(width = 1)) +  # Adjust dodge.width as needed
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper), position = position_dodge(width = 1)) +
  theme_minimal() +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(
    title = "Calculation of Confidence Intervals for Model Parameters",
    y = "Estimate",
    color = "Treatment") +
  scale_color_manual(values = c("cyan3", "orange")) +
    theme(
    axis.title.y = element_text(size = 6),
    axis.text.x = element_text(size = 6),  # Adjust the size of the x-axis labels
    axis.text.y = element_text(size = 6),  # Adjust the size of the y-axis labels
    strip.text = element_text(size = 10, face = "bold"),  # Bold facet wrap headers
    legend.text = element_text(size = 6),  # Adjust the size of legend text
    legend.title = element_text(size = 8, face = "bold"))  # Bold legend title

#Extracting TPC parameters 

sharpeschool_high_extra_params <- calc_params(sharpeschool_high_fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

sharpeschool_high_ci_extra_params <- Boot(sharpeschool_high_fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(sharpeschool_high_fit_nlsLM)), R = 1000, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

sharpeschool_high_pH_ci_extra_params <- left_join(sharpeschool_high_ci_extra_params, sharpeschool_high_extra_params)
sharpeschool_high_pH_TPC_parameters <- as_tibble(sharpeschool_high_pH_ci_extra_params)%>% 
  mutate(Treatment="Ambient")

sharpeschool_low_extra_params <- calc_params(sharpeschool_low_fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

sharpeschool_low_ci_extra_params <- Boot(sharpeschool_low_fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(sharpeschool_low_fit_nlsLM)), R = 1000, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')
  
sharpeschool_low_pH_ci_extra_params <- left_join(sharpeschool_low_ci_extra_params, sharpeschool_low_extra_params)
sharpeschool_low_pH_TPC_parameters <- as_tibble(sharpeschool_low_pH_ci_extra_params) %>% 
  mutate(Treatment="Low")

#Presenting TPC parameter data as a table 
sharpeschool_TPC_parameters <- full_join(sharpeschool_high_pH_TPC_parameters, sharpeschool_low_pH_TPC_parameters) 
as_tibble(sharpeschool_TPC_parameters)
  
#selecting for parameters we want for the figures
sharpeschool_graph_TPC_parameters <- sharpeschool_TPC_parameters %>% 
  subset(param %in% c('ctmin', 'ctmax', 'topt', 'rmax', 'breadth', 'e', 'eh', 'q10'))

sharpeschool_graph_TPC_parameters %>% pivot_wider(names_from=Treatment, values_from=c(conf_lower, conf_upper, estimate))
  

# TPC parameters plot
ggplot(sharpeschool_graph_TPC_parameters, aes(forcats::fct_relevel(Treatment), estimate, color = Treatment)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw(base_size = 12) +
  facet_wrap(~param, scales = 'free') +
  scale_x_discrete('', labels = function(x) stringr::str_wrap(x, width = 10)) +
  labs(title = 'Calculation of Confidence Intervals Between
       Thermal Performance Parameters',
       x = 'Treatment',
       y = 'Estimate',
       color = 'Treatment') +
  scale_color_manual(values = c("orange", "cyan3")) +  # Set colors as orange and blue
  theme(plot.title = element_text(hjust = 0.5))  # Center the plot title


```


